Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-07-14 doc/main_jfm.tex
finishing up revisions on section 2

\subsection{Time Marching and Nondimensionalizations}
From the mobility problem, we obtain translational and angular velocities of the $N_b$-body system.
A second order Adam-Bashforth scheme updates the particle positions and orientations.
dynamics but body collisions may occur during the simulation while a relatively large time step is chosen.
We therefore impose a short range repulsion that it will be turned on when the distance between two boundary points on different bodies are within one characteristic length.

For a two-dimensional vesicle, we denote a constant initial radius $R_0$ and 
the dimensionless shear rate is
\begin{equation}
\chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{equation}
%
where $\dot\gamma$ the shear rate, $\kappa$ the bending rigidity, and $\mu$ the fluid viscosity~\cite{Finken08}.

@@

%%%
\section{\label{IEM}Integral Equation Method}
Since the fluid velocity is assumed to be Stokesian, it can be written
in terms of layer potentials. Following previous work of~\cite{Lukas19},
we represent the velocity as the sum of a double-layer potential and the
$N_b$ Stokeslets and Rotlets
\begin{align}
  \label{eqn:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
torque-free and has force $\FF$, and the Rotlet force-free and has
torque $T$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
and imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, Stokeslet strength, $\FF_i$, and Rotlet strength $T_i$
satisfy
\begin{alignat}{3}
  \nonumber
  \vv_j + \omega_j (\xx - \aa_j)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eqn:SKIE}
    &+ \sum_{i=1}^{N_b} 
    \left(\SS(\xx,\aa_i) \FF_i + \RR(\xx,\aa_i) T_i\right),
    \quad &&\xx \in \bd \Gamma_j, \\
  \label{eqn:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, ds &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eqn:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu ds &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}
%
%The mobility problem for $N_b$-body system in a Stokes flow leads to a second-kind boundary integral equations (BIE) with a density function $\eta({\bf x}$ that is given by \cite{Lukas19}
%\begin{equation}
%\label{mobility}
%\begin{aligned}
%{\bf v}_i + &\omega_i\times({\bf x}-{\bf a}_i)\\
% =& -\frac12\eta({\bf x}) + D[\eta]({\bf x}) \\
%&+ \sum_{i=1}^N\big({\bf S}({\bf x}, {\bf a}_i){\bf F}_i+ {\bf R}({\bf x}, {\bf a}_i)t_i\big)+{\bf u}_\infty, \quad {\bf x}\in\Gamma \\
%\end{aligned}
%\end{equation}
%%
%with two constraints 
%%
%\begin{center}
%\begin{equation}
%\label{mobility2}
%\int_{\partial \Gamma_i}\eta\cdot \nnu ds = {\bf 0},
%\end{equation}
%\end{center}
%%
%\begin{center}
%\begin{equation}
%\label{mobility3}
%\int_{\partial \Gamma_i}\eta\times({\bf x}-{\bf a}_i)\cdot \nnu ds ={\bf 0},
%\end{equation}
%\end{center}
%%
%where the two-dimensional Stokeslet and the Rotlet are
%%
%\begin{gather}
%{\bf S}({\bf x}, {\bf a}) = \frac{1}{4\pi}\left(-\log(|({\bf x}-{\bf a})|){\bf I}+\frac{({\bf x}-{\bf a})\otimes({\bf x}-{\bf a})}{|({\bf x}-{\bf a})|^2}\right) \\ 
%{\bf R}({\bf x},{\bf a})=\frac{({\bf x}-{\bf a})^\perp}{4\pi|({\bf x}-{\bf a})|^2}.
%\end{gather}
%
%Here ${\bf r}={\bf x}-{\bf a}$ and $\rho=|{\bf r}|$.
Given a collection of particles with forces and torques calculated from
the hydrophobic interactions and the short range repulsion,
equations~\eqref{eqn:SKIE}--\eqref{eqn:mobility2} form a solvable set of
integral equations for the translational velocities $\vv_i$, the angular
velocities $\omega_i$, and the density function $\eeta$.

>>>>

\subsection{Time Marching and Nondimensionalizations}
By solving the mobility problem, we obtain translational and angular
velocities of the $N_b$-body system. A second-order Adam-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eqn:REPULforce} and
torque~\eqref{eqn:REPULtorque}, particle collisions are avoided even
when using a relatively large time step.

For a two-dimensional vesicle, we denote a constant initial radius $R_0$
and the dimensionless shear rate is
\begin{align}
  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the shear rate, $\kappa$ the bending rigidity, and
$\mu$ the fluid viscosity~\cite{Finken08}.

@@

%%%
\section{Integral Equation Method}
\label{sec:IEM}
Since the fluid velocity is assumed to be Stokesian, it can be written
in terms of layer potentials. Following previous work of~\cite{Lukas19},
we represent the velocity as the sum of a double-layer potential and the
$N_b$ Stokeslets and Rotlets
\begin{align}
  \label{eqn:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
torque-free and has force $\FF$, and the Rotlet force-free and has
torque $T$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
and imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, Stokeslet strength, $\FF_i$, and Rotlet strength $T_i$
satisfy
\begin{alignat}{3}
  \nonumber
  \vv_j + \omega_j (\xx - \aa_j)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eqn:SKIE}
    &+ \sum_{i=1}^{N_b} 
    \left(\SS(\xx,\aa_i) \FF_i + \RR(\xx,\aa_i) T_i\right),
    \quad &&\xx \in \bd \Gamma_j, \\
  \label{eqn:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, ds &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eqn:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu ds &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}
%
%The mobility problem for $N_b$-body system in a Stokes flow leads to a second-kind boundary integral equations (BIE) with a density function $\eta({\bf x}$ that is given by \cite{Lukas19}
%\begin{equation}
%\label{mobility}
%\begin{aligned}
%{\bf v}_i + &\omega_i\times({\bf x}-{\bf a}_i)\\
% =& -\frac12\eta({\bf x}) + D[\eta]({\bf x}) \\
%&+ \sum_{i=1}^N\big({\bf S}({\bf x}, {\bf a}_i){\bf F}_i+ {\bf R}({\bf x}, {\bf a}_i)t_i\big)+{\bf u}_\infty, \quad {\bf x}\in\Gamma \\
%\end{aligned}
%\end{equation}
%%
%with two constraints 
%%
%\begin{center}
%\begin{equation}
%\label{mobility2}
%\int_{\partial \Gamma_i}\eta\cdot \nnu ds = {\bf 0},
%\end{equation}
%\end{center}
%%
%\begin{center}
%\begin{equation}
%\label{mobility3}
%\int_{\partial \Gamma_i}\eta\times({\bf x}-{\bf a}_i)\cdot \nnu ds ={\bf 0},
%\end{equation}
%\end{center}
%%
%where the two-dimensional Stokeslet and the Rotlet are
%%
%\begin{gather}
%{\bf S}({\bf x}, {\bf a}) = \frac{1}{4\pi}\left(-\log(|({\bf x}-{\bf a})|){\bf I}+\frac{({\bf x}-{\bf a})\otimes({\bf x}-{\bf a})}{|({\bf x}-{\bf a})|^2}\right) \\ 
%{\bf R}({\bf x},{\bf a})=\frac{({\bf x}-{\bf a})^\perp}{4\pi|({\bf x}-{\bf a})|^2}.
%\end{gather}
%
%Here ${\bf r}={\bf x}-{\bf a}$ and $\rho=|{\bf r}|$.
Given a collection of particles with forces and torques calculated from
the hydrophobic interactions and the short range repulsion,
equations~\eqref{eqn:SKIE}--\eqref{eqn:mobility2} form a solvable set of
integral equations for the translational velocities $\vv_i$, the angular
velocities $\omega_i$, and the density function $\eeta$.
